[Re] Non-additive coupling enables propagation of synchronous spiking activity in purely random networks

### 2018-03-06 article/Caze_2018.tex
Rewrite the description of the differences in the semi-analytical solution

Finally, we looked at the evolution of synchronous group sizes for one combination of synaptic weights ($w_\text{ex}=w_\text{in}=\SI{0.2}{\milli\volt}$) in detail (Fig.~\ref{fig:markov}). The results confirms our previous conclusion that we can faithfully replicate the network behaviour. They match both qualitatively and quantitatively, the group size consistently declines with each iteration in linearly coupled networks (Fig.~\ref{fig:markov}A), whereas it increases for intermediate group sizes and declines otherwise in non-linearly coupled networks (Fig.~\ref{fig:markov}B). While the semi-analytic solution (red dotted line) shows a good match to the numerical results (grey lines, means as green dots), it shows some quantitative differences to the semi-analytic solution presented in Fig.~4 of the original article. In particular, our semi-analytical solution seems to mostly slightly underestimate the size of the group in the next iteration while the semi-analytical solution presented in the original article seems to slightly overestimate it.

>>>>

Finally, we looked at the evolution of synchronous group sizes for one combination of synaptic weights ($w_\text{ex}=w_\text{in}=\SI{0.2}{\milli\volt}$) in detail (Fig.~\ref{fig:markov}). The results confirms our previous conclusion that we can faithfully replicate the network behaviour. They match both qualitatively and quantitatively, the group size consistently declines with each iteration in linearly coupled networks (Fig.~\ref{fig:markov}A), whereas it increases for intermediate group sizes and declines otherwise in non-linearly coupled networks (Fig.~\ref{fig:markov}B). While the semi-analytic solution (red dotted line) shows a good match to the numerical results (grey lines, means as green dots), it shows some quantitative differences to the semi-analytic solution presented in Fig.~4 of the original article. The semi-analytical solution in the original article consistently overestimates the size of the group in the next iteration compared to the numerical solution. In contrast, our semi-analytical solution consistently underestimates their size in linearly coupled networks (Fig.~\ref{fig:markov}A). For non-linearly coupled networks, our solution underestimates the evolution of the group size for initial group sizes up to about 115--125 and only overestimates it for higher initial group sizes.
